### 2021-02-16 abstract.tex
abstract: Remove trailing whitespace
Add some commas to divide long compound sentences
Guidelines:
https://www.thepunctuationguide.com/comma.html#commasbasedonsentencestructure

Recommended by Writefull: https://revise-cvut-cz.writefull.ai/

State-of-the-art superposition-based theorem provers for \acrlong{fol}
rely on \glspl{sot} to constrain the applicability of inference rules 
which in turn shapes the ensuing search space.
The popular Knuth-Bendix simplification ordering is parameterized by 
a \emph{symbol precedence}---a permutation of the predicate and function symbols
of the input problem's signature.
The choice of the precedence thus has an indirect yet often substantial impact 
on the amount of work required to successfully complete a proof search.

@@

This paper describes and evaluates a symbol precedence recommender,
a machine learning system which estimates the best possible precedence
based on observations of prover performance on a set of problems and random precedences.
Using the graph convolutional neural network technology
the system does not presuppose the problems to be related or share a common signature. 
When coupled with the theorem prover Vampire and evaluated on the \acrshort{tptp} problem library
the recommender is found to outperform a state-of-the-art heuristic by more than \SI{2}{\percent}.

>>>>

State-of-the-art superposition-based theorem provers for \acrlong{fol}
rely on \glspl{sot} to constrain the applicability of inference rules,
which in turn shapes the ensuing search space.
The popular Knuth-Bendix simplification ordering is parameterized by 
a \emph{symbol precedence}---a permutation of the predicate and function symbols
of the input problem's signature.
The choice of the precedence thus has an indirect yet often substantial impact
on the amount of work required to successfully complete a proof search.

@@

This paper describes and evaluates a symbol precedence recommender,
a machine learning system which estimates the best possible precedence
based on observations of prover performance on a set of problems and random precedences.
Using the graph convolutional neural network technology,
the system does not presuppose the problems to be related or share a common signature. 
When coupled with the theorem prover Vampire and evaluated on the \acrshort{tptp} problem library,
the recommender is found to outperform a state-of-the-art heuristic by more than \SI{2}{\percent}.
